---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rcristin

<!-- badges: start -->
<!-- badges: end -->

rcristin is a simple R interface to query the [API for the Cristin database](https://api.cristin.no/v2/doc/index.html) for Cristin results, with error handling and automatic pagination. It (currently) consists of two functions: one for retrieving registered Cristin results and one for their associated author affiliation information. Both functions always return a data frame.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("henrikkarlstrom/rcristin")
```

## Example

A simple query for academic publications from a unit, which is stored as a data frame:

```{r example}
library(rcristin)
## get Cristin results from NTNU's University Library
ntnuub <- get_cristin_results(
  unit = "194.14.30.0", 
  published_since = 2015
  )
```

This can now be used for all sors of bibliometric analyses. Here is a table of the ten most common publication categories for the University Library of NTNU:

```{r cars}
table <- dplyr::count(ntnuub, category_name_en, sort = TRUE)

knitr::kable(head(table, 10), col.names = c("Cristin category", "Number of Cristin posts"))
```

And here is a graph of the Open Access status of the academic publications of the library:

```{r oa_graph}
# Filtering out the non-academic results
ntnuub <- ntnuub[ntnuub$category_code %in% c(
  "ACADEMICREVIEW", "ANTHOLOGYACA", "ARTICLE",
  "CHAPTERACADEMIC", "MONOGRAPHACA"), ]

# Giving the OA categories better names
ntnuub$open_access <- dplyr::recode(ntnuub$open_access,
                                    none = "Not archived",
                                    green = "Archived",
                                    gold = "Gold OA")

# Plotting
ggplot2::ggplot(
  data = ntnuub,
  ggplot2::aes(
    x = year_published,
    fill = forcats::fct_relevel(
      open_access, c("Gold OA", "Archived", "Not archived"))
    )
  ) +
  ggplot2::geom_bar() +
  ggplot2::geom_hline(yintercept = 0,
             size = 1,
             colour = "#565657") +
  ggplot2::labs(
    title = "Open Access status, NTNU University Library publications",
    subtitle = "2015-2020",
    x = NULL,
    y = NULL
    ) +
  ggplot2::theme_minimal() +
  ggplot2::theme(
    plot.title.position = "plot",
    legend.title = ggplot2::element_blank(),
    legend.text = ggplot2::element_text(size = 12,
                                   color = "#565657"),
    axis.ticks = ggplot2::element_blank(),
    panel.grid.minor = ggplot2::element_blank(),
    panel.grid.major.y = ggplot2::element_line(color="grey95"),
    panel.grid.major.x = ggplot2::element_blank(),
    panel.background = ggplot2::element_blank()
    ) +
  ggplot2::ylim(0, 15) +
  ggplot2::scale_fill_manual(
    values = c("#f7d019", "forestgreen", "grey85")
    )
```

